### 2014-11-11 report/preamble.tex
Add normalized occurance count graph for Disconnect organization counts

\pgfplotsset{datasetsCDF/.style=
{	
xmin=0,
xmax=1,
ymin=0,
ymax=1,
grid=both,
xtick={0,.1,...,1.1},
ytick={0,.1,...,1.1},
enlargelimits=false,
% Marks 0% and 99%.
mark repeat=99,
legend pos=south east,
legend style={
cells={anchor=west},
},
},
datasetsCDFFullPage/.style=
{	
width=\textwidth,
height=1.425\textwidth,
}
}

>>>>

\pgfplotsset{datasetsCDF/.style=
{
xmin=0,
xmax=1,
ymin=0,
ymax=1,
grid=both,
xtick={0,.1,...,1.1},
ytick={0,.1,...,1.1},
enlargelimits=false,
% Marks 0% and 99%.
mark repeat=99,
legend pos=south east,
legend style={
cells={anchor=west},
},
},
datasetsCDFFullPage/.style=
{
width=\textwidth,
height=1.41\textwidth,
}
}

\pgfplotsset{datasetsOccurances/.style=
{
ymin=,
xmin=0.1,
xmax=100,
xtick={0.1,1,2,3,4,5,10,20,50,100},
minor xtick={6,7,8,9,30,40,60,70,80,90},
xticklabel={%
	\ifnum\ticknum=9%
		$100^+$%
	\else%
		\pgfmathfloatparsenumber{\tick}%
		\pgfmathfloatexp{\pgfmathresult}%
		\pgfmathprintnumber[fixed,precision=0]{\pgfmathresult}%
	\fi%
},
yticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill,
/pgf/number format/precision=2
},
% Marks 0.1.
mark repeat=1,
mark indices={1},
}
}
